Cosmological constraints from the redshift dependence of the volume effect using the galaxy 2-point correlation function across the line-of-sight

### 2017-04-01 draft/draft2.tex
updates

\begin{abstract}
{\bf Let us use 1) angular CF across the line-of-sight 2) $\xi_{\bot}$ rather than $\omega_{r_{\bot}}$}
We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the angular 2pCF shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig4_a.eps}
   \includegraphics[width=16cm]{fig4_b.eps}
   \includegraphics[width=16cm]{fig4_c.eps}
   \includegraphics[width=16cm]{fig4_d.eps}
   }
   \caption{\label{fig_sys}
  First row: $\omega_{r_\perp}$ (left), $\hat{\omega}_{r_\perp}$ (middle), and $\hat\omega_{r_\perp}(z=z_i)-\hat\omega_{r_\perp}(z=0)$ (right) calculated with the RSD effect included.
  Second row: $\omega_{r_\perp}$ (left) and $\hat{\omega}_{r_\perp}$ (middle) are shown for four different halo-mass-cuts, $3\times 10^{11},~1\times 10^{12},~4\times 10^{12},~\&~1\times 10^{13}~M_\odot$, 
  below which we remove from 2pCF calculation. 
  The right panel shows the difference in $\hat{\omega}_{r_\perp}$ between the $3\times 10^{11}~M_\odot$ mass-cut case and the other mass-cut cases. 
  Third row: The same as the second row panels, except that the RSD effect is considered.
  Fourth row: The redshift evolution in case of using {\it samples with constant number density} $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
  and the RSD effect is considered. } 
\end{figure*}

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
   \includegraphics[width=8cm]{fig9_a.eps}
   \includegraphics[width=8cm]{fig9_b.eps}
   }
   \caption{\label{fig_contours}
   Left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
   the method can lead to very tight cosmological constraint.
   Right: The constraints in case that one or two high redshift bins are not used. 
   }
\end{figure*}

@@

Finally, the fourth row of the Figure displays the 
redshift evolution in case of using samples with constant number density $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
with the RSD effect considered. %(the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample).
We see the redshfit evolution of $\hat \omega_{r_\perp}$ is as small as $\lesssim3\%$.

@@

We constrain $\Omega_m$ and $w$ through a Bayesian analysis (\cite{Bayesian}; also see \cite{LB2002,Li2016}).
We assume that the likelihood takes the form
\begin{equation}\label{eq:like}
 \mathcal{L} \propto \exp\left[-\frac{\chi^2}{2}\right],
\end{equation}
and scan the parameter space in the $\Omega_m-w$ plane to obtain the 68.3\% and 95.4\% CL regions.
The result is displayed in the left panel Figure \ref{fig_contours}.

@@

In case that we do not have high redshfit galaxies, the constraint becomes weaker.
Figure \ref{fig_contours} displays that, 
in case that we only use the galaxies at $z=$0, 0.5 and 1, 
the 2$\sigma$ uncertainties of $\delta\Omega_m\approx0.01,\\ \delta w\approx0.1$ (the other parameter fixed at its best-fit value).
The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0 and 0.5.

>>>>

\begin{abstract}
We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the angular 2pCF shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig4_a.eps}
   \includegraphics[width=16cm]{fig4_b.eps}
   \includegraphics[width=16cm]{fig4_c.eps}
   \includegraphics[width=16cm]{fig4_d.eps}
   }
   \caption{\label{fig_sys}
  First row: $\omega_{r_\perp}$ (left), $\hat{\omega}_{r_\perp}$ (middle), and $\hat\omega_{r_\perp}(z=z_i)-\hat\omega_{r_\perp}(z=0)$ (right) calculated with the RSD effect included.
  Second row: $\omega_{r_\perp}$ (left) and $\hat{\omega}_{r_\perp}$ (middle) are shown for four different halo-mass-cuts, $3\times 10^{11},~1\times 10^{12},~4\times 10^{12},~\&~1\times 10^{13}~M_\odot$, 
  below which we remove from 2pCF calculation. 
  The right panel shows the difference in $\hat{\omega}_{r_\perp}$ between the $3\times 10^{11}~M_\odot$ mass-cut case and the other mass-cut cases. 
  Third row: The same as the second row panels, except that the RSD effect is considered.
  Fourth row: The redshift evolution in case of using {\it samples with constant number density} $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
  and the RSD effect is considered (the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample). } 
\end{figure*}

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
   \includegraphics[width=12cm]{fig9.eps}
   }
   \caption{\label{fig_contours}
   Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
   the method can lead to very tight cosmological constraint.
   }
\end{figure*}

@@

Finally, the fourth row of the Figure displays the 
redshift evolution in case of using samples with constant number density $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
with the RSD effect considered. %(the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample).
We see the redshfit evolution of $\hat \omega_{r_\perp}$ is still as small as $\lesssim5\%$, similar to the case of using constant mass cut sample.

@@

We constrain $\Omega_m$ and $w$ through a Bayesian analysis (\cite{Bayesian}; also see \cite{LB2002,Li2016}).
We assume that the likelihood takes the form
\begin{equation}\label{eq:like}
 \mathcal{L} \propto \exp\left[-\frac{\chi^2}{2}\right],
\end{equation}
and scan the parameter space in the $\Omega_m-w$ plane to obtain the 68.3\% and 95.4\% CL regions.
The result is displayed in Figure \ref{fig_contours}.

@@

### 2017-04-01 draft/draft3.1.tex
updates

\begin{abstract}
We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured $\xi(r_{\bot})$.
Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

The upper-left panel of Figure \ref{fig_diffz} displays the 2pCF across the line-of-sight measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
We multiply $\xi$ by the separation $r_\perp$ to obtain a similar statistical uncertainty on all scales.
For convenience we will use the denotation
\begin{equation}
 \hat \xi_{r_{\perp}} \equiv r_{\perp} \xi.
\end{equation}

@@

The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
the higher the redshift, the greater the enhancement.%the amplitude monotonically increases as a function of redshift.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
   \includegraphics[width=8cm]{fig9_a.eps}
   \includegraphics[width=8cm]{fig9_b.eps}
   }
   \caption{\label{fig_contours}
   Left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
   based on the redshift evolution of the shape of the 2pCF across the line-of-sight  $\hat\xi_{r_\perp}$.
   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
   the method can lead to very tight cosmological constraint.
   Right: The constraints in case that one or two high redshift bins are not used. 
   }
\end{figure*}

@@

We vary the mass cut and check the effect of galaxy bias on $\hat \xi_{r_\perp}$.
The second row of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
are imposed to create samples with different galaxy biases.
The measured 2pCF across the line-of-sight are displayed.

@@

In summary, the effect of RSD and galaxy bias on the shape of the galaxy correlation function across the line-of-sight is not large, but is non-negligible.
When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.

@@

@@

In case that we do not have high redshfit galaxies, the constraint becomes weaker.
Figure \ref{fig_contours} displays that, 
in case that we only use the galaxies at $z=$0, 0.5 and 1, 
the 2$\sigma$ uncertainties of $\delta\Omega_m\approx0.01,\\ \delta w\approx0.1$ (the other parameter fixed at its best-fit value).
The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0 and 0.5.

@@

@@

This method is designed to be applied to current and future LSS surveys,
with a particular emphasis on {\it photometric surveys}.
The galaxy 2pCF across the line-of-sight in redshift shells is much less affected by the large redshift errors compared wit the 3D 2pCF.
DES will probe hundreds of millions of galaxies at $z\lesssim1.5$, 
and LSST will probe tens of billions of galaxies at $z\lesssim2$.
We expect very tight cosmological constraints from these surveys.
%and the redshift error will not quite affect the angular 2pCF measurement 
%as long as the redshift dependence of the photometric redshift can be reliably understood.

Our series of works \cite{Li2014,Li2015,Li2016}, together with this analysis, 
and also \cite{topology,MS2016},
are introducing a new strategy to constrain cosmology from galaxy clustering.
We utilize a statistical pattern which remains constant at all redshifts;
this invariance is broken when incorrect cosmologies are adopted to construct the galaxy distribution
and introduces redshift evolution of geometric distortion.
The systematic effects can be corrected by performing a N-body simulation 
in a cosmology with values of parameters close enough to the underlying correct one.
This avoids the difficulty in the analytical modeling the galaxy clustering, galaxy bias and RSD,
and enables reliable cosmological constraint on relatively small clustering scales.
We hope these methods play an important role in deriving cosmological constraints from future LSS surveys.

@@

%\bibitem[Ade et al. (2015)]{Planck2015}
%Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

@@

%\bibitem[Anderson et al.(2013)]{Anderson2013}
%Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

@@

%\bibitem[Betoule et al.(2014)]{JLA}
%Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

%\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

@@

%\bibitem[Riess et al.(2011)]{Riess2011}
%Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera

@@

%\bibitem[Ross et al.(2015)]{MGS}
%Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835

>>>>

\begin{abstract}
We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured $\xi(r_{\bot})$.
Using mock galaxy catalogues (containing hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

The upper-left panel of Figure \ref{fig_diffz} displays the 2pCF across the line-of-sight measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
We multiply $\xi$ by the separation $r_\perp$ to obtain a similar statistical uncertainty on all scales.
For convenience we will use the denotation
\begin{equation}
 \xi_{r_{\perp}} \equiv r_{\perp} \xi.
\end{equation}

@@

The mis-scaling not only changes the shape of the 2pCF but also changes the value of $ \xi_{r_\perp}$. %The amplitude of $r_\perp\xi$ is amplified due to the stretch of scale.
As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
the higher the redshift, the greater the enhancement
\footnote{The value of $\xi$ is not affected by the mis-scaling. 
But since we are using $r_\perp\xi$ rather than $\xi$, the y-axis values are affected. 
For a 20\% up-rescaling, the peak value of $r_\perp\xi$ is also increased by 20\%.}.%the amplitude monotonically increases as a function of redshift.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
   \includegraphics[width=8cm]{fig9_a.eps}
   \includegraphics[width=8cm]{fig9_b.eps}
   \includegraphics[width=8cm]{fig9_c.eps}
   \includegraphics[width=8cm]{fig9_d.eps}
   }
   \caption{\label{fig_contours}
   Upper left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
   The green point denotes our fiducial cosmological model and the contours denote the statistical error.
   Utilizing the HR4 snapshots data (containing hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2),
   the method lead to very tight cosmological constraint.
   Upper right: The constraints in case that one or two high redshift bins are not used.
   Lower left: The 95.4\% likelihood contours using different clustering scales.
   Lower right: A comparison of the constraint with the cosmological constraints from the current observational data.
   }
\end{figure*}

@@

We vary the mass cut and check the effect of galaxy bias on $\hat \xi_{r_\perp}$.
The second row of Figure \ref{fig_sys} displays the 2pCF measured from galaxies within a $3150\times3150\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshot.
Four values of minimal mass limits, $3\times 10^{11} M_{\odot}$, $1\times 10^{12} M_{\odot}$, $4\times 10^{12} M_{\odot}$ and $1\times 10^{13} M_{\odot}$,
are imposed to create samples with different galaxy biases.
The measured 2pCF across the line-of-sight are displayed.

@@

%In summary, the effect of RSD and galaxy bias on the shape of the galaxy correlation function across the line-of-sight is not large, but is non-negligible.
%When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
%so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.

@@

\subsubsection{More discussion}

In summary, we aim to minimise the redshift evolution of the shape of the normalised angular 2pcf; 
the shape change is dramatic when considering a cosmology much deviated from the fiducial model.
However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. 
These systematics are removed with the aid of simulations.
The procedure of the correction of systematics is similar to what was implemented in our previous papers \cite{Li2014,Li2015,Li2016}.

The systematics are estimated from a simulation conducted using a particular cosmology. 
There could be a bias in the estimation if the simulation cosmology is different from the truth. 
The bias would not be serious if the simulation cosmology turns out to be consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
In the case that there is a large discrepancy between the simulation cosmology and the best-fit cosmology, one needs to adjust the simulation cosmology and re-do the analysis.

A more precise approach would involve estimating the systematic effect from a set of simulations covering the relevant volume of the parameter space. 
This would remove the remaining uncertainty associated with the cosmological dependence. 
This approach would also enable the estimation of the $systematic\ error$, 
which could be important when the sample size is large enough and the systematic error becomes as small as the $statistical\ error$.

The third row of Figure \ref{fig_sys} shows that, 
if having a large difference in bias between the samples,
there is a large systematic variation on small scales. 
This means that an accurate modelling of systematics from simulations is required. 
To avoid the possible difficulty, one can conduct the analysis using a volume-limited sample, 
where the redshift evolution of galaxy properties is small and the systematic effect from RSD and galaxy bias is also small,
as shown by the fourth row of Figure \ref{fig_sys}.

To avoid the large systematics in the nonlinear regime, 
another solution would be to increase the scale of analysis to larger separations where the non-linear effect is becoming subdominant. 
Figure \ref{fig_sys} shows that, 
on scales of $s=20-50 h^{-1} {\rm Mpc}$ the systematic effect is 2-3 times smaller than that of $s=5-20 h^{-1} {\rm Mpc}$. 
Actually, we tested and found that, using $s = 5-40 h^{-1} {\rm Mpc}$ and $20-40 h^{-1} {\rm Mpc}$, 
yields cosmological constraints that are pretty close to each other (see \S 4).

We do not consider the systematic effects in case of non-standard cosmological scenarios such as modified gravity and warm dark energy. 
These topics go beyond the scope of this work, and they are worthy future investigations.

@@

The simulation sample used in this analysis reaches $z=2$.
The constraint becomes weaker if we limit the highest redshift of the samples.
The upper right panel displays that, 
in case that we exclude the $z=2$ galaxies, 
the 2$\sigma$ uncertainties of $\delta\Omega_m\approx0.01,\\ \delta w\approx0.1$ (the other parameter fixed at its best-fit value).
The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0, 0.5 and 1.

So far we simply follow the convention of \cite{Li2016} and adopts $5\hMpc <s< 40\hMpc$. 
As discussed in the \S 4.3.3, one may want to avoid large systematics in the non-linear regime. 
In this case one can adopt $20\hMpc<s<40\hMpc$,
which significantly reduces the systematic effects while not much weaken the power of the final constraints,
as shown by the lower left panel of Figure \ref{fig_contours}.

The choice of the redshift width $105 \hMpc$ is also slightly little arbitrary. 
It should be larger than the distance distortion from the RSD and redshift errors.
The optimistic scheme of clustering scales and redshift width should depend on the specific galaxy sample used in the analysis. 
One could adjust them to have a good balance between the power of cosmological constraint and the size of systematic effect.

Finally, to be connected with the real observations, 
the lower right panel displays the constraints from Planck CMB (dotted blue, \cite{Planck2015}),
the AP analysis using BOSS DR12 galaxies (solid magenta, \cite{Li2016}),
and the joint constraint $\Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$ 
obtained using the CMB+SNIa+BAO+AP (dashed black, \cite{6dFGS,MGS,Riess2011,JLA,Anderson2013,Li2016}).

The predicted constraints from this method clearly wins due to the large sample size.
The total number of galaxies used in this work is 1,749 million,
which is 1,000 times of the BOSS DR12 sample size.
So the constrained area is also $\sim 30$ times smaller.
Such a large sample size will be enabled by LSST (the Large Synoptic Survey Telescope) \footnote{https://www.lsst.org/}, 
which probe tens of billions of galaxies at $z\lesssim2$.

%combined with an AP analysis using BOSS DR12 galaxies. This represents the current scenario of cosmological constraints from observations. A new plot is added to compare it with the constraint from our method.
%the JLA SNIa sample (green area, ),
%the BAO measurement from BOSS DR11 galaxies (bright yellow, ),
%\footnote{The CMASS and LOWZ samples from BOSS DR11 have a sky coverage of 8\,377 $\rm deg^2$ and a completeness of 97\%.
%They are very close to the DR12 samples.},
%a combination of the BOSS DR11 BAO and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ (dark yellow, ),
%and the full-mission Planck observations of temperature and polarization anisotropies, released in 2015 (blue, \cite{Planck2015})

@@

In our early work of \cite{Li2015,Li2016}, 
we proposed to use the angular-dependence of the galaxy clustering to apply an AP test and derive cosmological constraints. 
In contrast, in this work we focus on the scale-dependence of the clustering. 
The two methods focus on different parts of the clustering information, and the constraints derived from the them should be fairly independent.
But it is still suggested to have an estimation of the covariance between them in case one is using both methods to do an analysis. 
An alternative way is to investigate the redshift evolution of the correlation map $\xi(s,\mu)$ as a function of both scale and direction, which captures all the information.

@@

This method is designed to be applied to current and future LSS surveys,
with a particular emphasis on {\it photometric surveys}.
The galaxy 2pCF across the line-of-sight in redshift shells is much less affected by the large redshift errors compared wit the 3D 2pCF.
The Dark Energy Survey will probe hundreds of millions of galaxies at $z\lesssim1.5$
\footnote{https://www.darkenergysurvey.org/}, 
and LSST will probe tens of billions of galaxies at $z\lesssim2$.
We expect very tight cosmological constraints from these surveys.
%and the redshift error will not quite affect the angular 2pCF measurement 
%as long as the redshift dependence of the photometric redshift can be reliably understood.

Our series of works \cite{Li2014,Li2015,Li2016}, together with this analysis, 
and also \cite{topology,MS2016},
are introducing a new strategy to constrain cosmology from galaxy clustering.
We utilize a statistical pattern which remains constant at all redshifts;
this invariance is broken when incorrect cosmologies are adopted to construct the galaxy distribution
and introduces redshift evolution of geometric distortion.
The systematic effects can be corrected by performing an N-body simulation 
in a cosmology with values of parameters close enough to the underlying correct one.
This avoids the difficulty in the analytical modeling the galaxy clustering, galaxy bias and RSD,
and enables reliable cosmological constraint on relatively small clustering scales.
We hope these methods play an important role in deriving cosmological constraints from future LSS surveys.

@@

\bibitem[Ade et al. (2015)]{Planck2015}
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

@@

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

@@

\bibitem[Betoule et al.(2014)]{JLA}
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

@@

\bibitem[Riess et al.(2011)]{Riess2011}
Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119
%A 3\% Solution: Determination of the Hubble Constant with the Hubble Space Telescope and Wide Field Camera

@@

\bibitem[Ross et al.(2015)]{MGS}
Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835
